Drones in Wind

### 2017-08-09 Papers/DroneInTheWind.tex
Update DroneInTheWind.tex

OptimTraj  was used to find the time-optimal trajectory for 5 different paths, all starting at the origin. 
Namely, the 5 paths ended at (1,1), (2,2), (3,3), (4,4), and (5,5). This is so that we can see how the model actually changes behaviors over these different paths. Ultimately, the results will be compared to \textbf{one} of D'Andrea's results \textcolor{red}{Citation Needed}, which took the path from (0,0) to (5,5).  All plots will be shown alongside D'Andrea's for comparison.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                                OptimTraj  Analysis                                                                         %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{OptimTraj Analysis}
\begin{quote}
\begin{lstlisting}
load('traj.mat')
t = t;
x = x(1,:);
xd= x(2,:);
z = x(3,:);
zd= x(4,:);
th= x(5,:);
w = u(1,:);
f = u(2,:);
\end{lstlisting}
\end{quote}
The values for all 5 instances were unpacked and subsequently plotted over time.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                                Simulation Analysis                                                                         %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Simulation Analysis}
\begin{quote}
\begin{lstlisting}
load('data1.mat')
t = processdata.t;
x = processdata.x;
xd = processdata.xdot;
z = processdata.z;
zd = processdata.zdot;
th = processdata.theta;
f = controllerdata.actuators.thrust;
w = controllerdata.actuators.pitchrate;
\end{lstlisting}
\end{quote}
Similarly, the simulations were also unpacked and plotted over time.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                              D'Andrea Results                                                                        %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{D'Andrea Results}

>>>>

In this section, the trajectory for $x=5,z=5$ was analyzed. First the Optimal trajectory was calculated and saved, then the simulation was run and data stored, and finally both results were plotted against each other. To reiterate, \textbf{Solid lines} are to show the optimal trajectory, and \textbf{dashed lines} show the simulated quad-rotor path.

Ultimately, the results will be compared to \textbf{one} of D'Andrea's results \textcolor{red}{Citation Needed}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                                Simulation Analysis                                                                         %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Simulation Analysis}
\begin{quote}
\begin{lstlisting}
load traj
topt = t;
xopt = x;
uopt = u;

load data
tsim = processdata.t;
xsim = [processdata.x; processdata.xdot; processdata.z; processdata.zdot;    processdata.theta];
usim = [controllerdata.actuators.pitchrate;...
	controllerdata.actuators.thrust];
\end{lstlisting}
\end{quote}
The preceding lines of code are meant to show how easily the data can be unpacked and plotted against each other. Below, \textcolor{blue}{\textbf{Figure X} shows the optimal and actual state of the quadrotor and \textbf{figure Y} shows the optimal and actual inputs of the quadrotor.}

\begin{figure}[h!]
  \centering
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{State.png}
    \caption{Quadcopter state over time.}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{Inputs.png}
    \caption{Quadcopter Inputs over time.}
  \end{minipage}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                          Comparison with D'Andrea Results                %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison with D'Andrea Results}

We can compare the simulated trajectory with that of \textit{Performance benchmarking of quadrotor systems using time-optimal control}. \textcolor{red}{Citation}
